Self-tunable approximated explicit MPC: Heat exchanger implementation and analysys

### 2023-01-27 paper/elsarticle/main.tex
GITIGNORE and clean-up

The main benefit in form of lower computational complexity in the control phase comes hand in hand with a non-negligible drawback. The size of the parametric solution may increase to the value that it becomes impractical to utilize for two reasons: (i) memory footprint is higher than the available memory size of the control unit, and (ii) the computational time associated with finding the optimal control action is higher than the available time period for control action implementation. Although this control strategy has its challenges, it is still very beneficial for practical usage for its benefits.

\section{Preliminaries}
\label{sec:preliminaries}
In this section, the theoretical background necessary for this work is summarized. First, the explicit model predictive control is recalled. Next, the tunable technique of the approximated explicit model predictive control is introduced. Last but not least, the ideas of self-tunable technique of the approximated explicit MPC are presented.

>>>>

The main benefit in form of lower computational complexity in the control phase comes hand in hand with a non-negligible drawback. The size of the parametric solution may increase to the value that prevents its real-time implementation for two reasons: (i) memory footprint is higher than the available memory size of the control unit, and (ii) the computational time associated with finding the optimal control action is higher than the available time period for control action implementation. Although this control strategy has its challenges, it is still very beneficial for practical usage for its benefits.

[TODO: Please, write a paper structure]

The paper is organized as follows...

\section{Theoretical backgrounds}
% \section{Preliminaries}
\label{sec:preliminaries}

In this section, the theoretical backgrounds necessary for the proposed method  work is summarized. First, the explicit model predictive control is recalled. Next, the tunable technique of the approximated explicit model predictive control is introduced. Last but not least, the ideas of self-tunable technique of the approximated explicit MPC are presented.
